---
title: "This is your first **Quarto** document"
author: "Matteo Chialva & Martino Adamo"
date: "2024-01-24"
format:
  html:
    code-fold: true
    toc: true
    toc-title: Contents
    toc-location: left
    embed-resources: true
bibliography: citations.bib
---

## Results 1

::: panel-tabset
### Tab One

Hey! I'm the first tab!

### Tab Two

Hey! I'm the second tab!
:::

## Results 2

::: {.panel-tabset .nav-pills}
### Tab One

Hey! I'm the first tab!

### Tab Two

Hey! I'm the second tab!
:::

## First Section

Here you can write your first paragraph. You can also add citations contained in 'citations.bib' file [@Hu-et-al]. See <http://rmarkdown.rstudio.com>.

You can embed an R code chunk like this:

```{r}
#| echo: true        # show or not the chunk
#| code-fold: true   # show or not the code-folding in this chunk
#| include: true      # show or not the code
#| output: true      # show the output of the function
summary(cars)
```

## Second section (Plots)

You can also embed plots, for example:

```{r}
#| echo: true
#| include: true
  
plot(pressure)

```

::: {layout="[ [1], [2,3] ]"}
```{r}
#| echo: true
#| include: true
#| fig-cap: "(A) Cars plot"
library(ggplot2)
plot(cars)
```

```{r}
#| echo: true
#| include: true
#| fig-cap: "(B) Pressure plot"
library(ggplot2)
plot(pressure)
```

```{r}
#| echo: true
#| include: true
#| fig-cap: "(C) Iris plot"
#| fig-cap-location: bottom
library(ggplot2)
ggplot(iris, aes(Species, Sepal.Width, fill=Species))+geom_boxplot()
```
:::

::: {layout-ncol="2"}
### List One

-   Item A
-   Item B
-   Item C

### List Two

-   Item X
-   Item Y
-   Item Z
:::

```{r}
#| echo: true
#| include: true
  
plot(pressure)

```

Note that the `echo: false` parameter was added to the code chunk to not include the code in the final rendered report:

```{r}
#| echo: false        # show or not the chunk
#| code-fold: false   # show or not the code-folding in this chunk
#| include: true      # show or not the code
#| output: false      # show the output of the function
library(dplyr)
```

You also can also enable the code-folding option (code-fold: false), or do not show the product of your code in the final report (output: false)

You can easily add citation using the visual editor and adding references from Zotero or other remote sources.

This is my first Zotero citation [@bravo2017].

This is my first R-package citation [@ggplot2].

## References
