---
title: "This is your first **RMarkdown** Presentation"
author: "Matteo Chialva & Martino Adamo"
date: "2024-01-24"
output: 
  revealjs::revealjs_presentation:
    transition: default
    self_contained: false
    reveal_plugins: 
      - search
      - zoom
      - notes
      - chalkboard
      - menu
    reveal_options:
      slideNumber: true
      chalkboard:
        theme: chalkboard
        toggleNotesButton: true
      menu:
        numbers: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## [R Markdown]{style="font-size: 60px; font-weight: bold; color:red;"}

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

<aside class="notes">
Here are some notes.
</aside>

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

# In the morning

## Getting up

- Turn off alarm
- Get out of bed

## Breakfast

- Eat eggs
- Drink coffee

## In the evening

# Dinner

- Eat spaghetti
- Drink wine

# Going to sleep

- Get in bed
- Count sheep
