---
title: "This is your first **RMarkdown** document"
author: "Matteo Chialva & Martino Adamo"
date: "2024-01-24"
output:
  html_document:
    theme: default #default, bootstrap, cerulean, cosmo, darkly, flatly, journal, lumen, paper, readable, sandstone, simplex, spacelab, united, and yeti.
    highlight: default #default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, textmate
    toc: yes
    toc_float: true
  pdf_document:
    toc: yes
bibliography: citations.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Results 1 {.tabset}

### Tab One

Hey! I'm the first tab!

### Tab Two

Hey! I'm the second tab!

## Results 2 {.tabset .tabset-pills}

### Tab One

Hey! I'm the first tab!

### Tab Two

Hey! I'm the second tab!

## First Section

Here you can write your first paragraph. You can also add citations contained in 'citations.bib' file [@Hu-et-al]. See <http://rmarkdown.rstudio.com>.

You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Second section (Plots)

You can also embed plots, for example:

```{r pressure, include=T, echo=T}
plot(pressure)
```

Note that the `echo = FALSE` parameter prevents printing of the R code that generated the plot.

```{r include=F}
library(rmarkdown)
```

You also can add silent code that won't be reported in your final report (include=F)

## References
